Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-09 volunteer-clouds-ieee-ci-si.tex
Graph with explanation

However, it is interesting to note why this is so, and the first hint
is the inter-experiment correlation between the number of IPs in
succesive experiments. While before it was an unremarkable 10\%, it is
now more than 43\%, making the numbef of IPs in contiguous experiments
highly correlated. The main reason for this is the setup in {\sf
  NodIO-W$^2$}, which restarts an island after a solution has been
found and also is running even if the tab is not on the
foreground. This means that volunteers can leave the experiment
running for as long as they want and they will be contributing to
experiment after experiment, unlike the previous version, where they
stopped contributing after the solution was found. This is also
reflected in the number of PUTs, which is the number of generations
divided by 100; more than 50\% of the volunteers run for more than
4000 generations. All things considered, this means than there are
many more computers running {\em simultaneously}, leading to this
almost 5-fold increase in running time. 
%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

>>>>

However, it is interesting to note why this is so, and the first hint
is the inter-experiment correlation between the number of IPs in
succesive experiments. While before it was an unremarkable 10\%, it is
now more than 43\%, making the numbef of IPs in contiguous experiments
highly correlated. The main reason for this is the setup in {\sf
  NodIO-W$^2$}, which restarts an island after a solution has been
found and also is running even if the tab is not on the
foreground. This means that volunteers can leave the experiment
running for as long as they want and they will be contributing to
experiment after experiment, unlike the previous version, where they
stopped contributing after the solution was found. This is also
reflected in the number of PUTs, which is the number of generations
divided by 100; more than 50\% of the volunteers run for more than
4000 generations. All things considered, this means than there are
many more computers running {\em simultaneously}, leading to this
almost 5-fold increase in running time.

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\linewidth]{img/ips-time-ww.png}
\caption{Time employed in every experiment vs. number of IPs (in abscises). The red dot and line show the average and standard deviation, the shade of blue the number of experiments with the same number of IPs. }  
\label{fig:ipstime:w2}
\end{figure}
%
It is also interesting to measure the scaling properties in this
model, that is, the relationship between the number of IPs
participating in an experiment and the time it takes to complete
it. This is shown in Figure \ref{fig:ipstime:ww}, which shows every
experiment in a time (in milliseconds) vs. number of workers participating
in it. Although there is not a clear trend, the graph seems to say
that the time needed for finding the solution in this evolutionary 
algorithm does not depend on the number of workers participating in
it. This does not mean that it is independent on the number of {\em
  simultaneous} users, which is probably the case although it is more
difficult to measure. There seems to be a trend towards a decreasing
standard deviation in the time, with more volunteers adding {\em
  robustness} to an experiment and certainty in the time it is taking;
however, more experiments would be needed to check this hypothesis.

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
